Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-29 newdraft.tex
added the paracpx. Lie algebroid stuff

\documentclass[letterpaper,12pt]{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{\marginparwidth}
\addtolength{\headwidth}{0.25in}
%----------------
%\setlength{\marginparwidth}{0pt} % width of margin notes
%\setlength{\marginparsep}{0pt} % width of space between body text and margin notes
\setlength{\evensidemargin}{0.125in} % Adds 1/8 in. to binding side of all 
\setlength{\oddsidemargin}{0.125in} % Adds 1/8 in. to the left of all pages
\setlength{\textwidth}{6.375in} % assuming US letter paper (8.5 in. x 11 in.) and 
\raggedbottom
\setlength{\parskip}{\medskipamount}
\renewcommand{\baselinestretch}{1}
%---------------------------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\sA}{\mathcal{A}}
\newcommand{\cO}{\mathcal{O}}
\def\d{{\rm d}}
\def\dbar{\Bar{\partial}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\bm{\p}}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\theoremstyle{remark}
\newtheorem{Ex}[theorem]{Example}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $[acksquare$}

\input xy

@@

This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like. First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle. The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
\begin{align*}
X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
\end{align*}
i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.

@@

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

@@

@@

There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we will call a Calabi-Yau manifold a K\"ahler manifold $(M,g,I)$ with the holonomy group of the underlying Riemannian metric to be $\text{Hol}(g)\subseteq SU(d)$, as opposed to $U(d)$, which is the case for ordinary K\"ahler manifolds.\footnote{Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.} A consequence of this property is that there exists a {\it holomorphic volume form}, i.e. a non-vanishing section $\Omega \in \Omega^{d,0}$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
\begin{align*}
    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega},
\end{align*}
where $\omega=gI$ is the K\"ahler form.

@@

Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form. We choose the local adapted coordinates $(x^i,\xt_j)$ in which $\eta$ and $\omega$ have the canonical form
\begin{align*}
    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i.
\end{align*}
Because the holonomy of $\eta$ is now contained in $SL(d)$, there is also a covariantly constant tensor $\hat{\Omega}$
\begin{align*}
    \hat{\Omega}=dx^1\w\cdots\w dx^d+d\xt_1\w\cdots\w d\xt_d=\Omega+\tl{\Omega},
\end{align*}
which satisfies $\pt\Omega=\p\tl{\Omega}=0$ as well as
\begin{align*}
   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
\end{align*}

We call $\hat{\Omega}=(\Omega,\tl{\Omega})$ a {\bf para-holomorphic volume form}. Remember that on a para-complex manifold $\PS$ of dimension $2n$, the appropriate analogue of the holomorphic forms are the para-holomorphic forms, given by pairs $(\alpha,\tl{\alpha})\in\Omega^{(k,0)+(0,k)}(\PS)$ (here the bigrading is with respect to the para-complex structure), satisfying $\pt\ap=\p\tl{\ap}=0$. Therefore, the {para-holomorphic volume form} is exactly the correct analogue of the holomorphic volume form in case of the Calabi-Yau manifolds. Furthermore, because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, and so it defines a volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and we see that the para-Calabi-Yau structure on $\PS$ augments the canonical foliations $M$ and $\Mt$ of the para-complex manifold with volume forms and both the foliation manifolds are consequently orientable.

@@

\begin{Ex}
If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
We will denote this dg manifold by $N_{\pd}$. 
To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$.
\brian{Relate to Lie algebroid description.}
\end{Ex}

@@

\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the Calabi-Yau geometry of $M$. Consider an affine manifold $B$ and take a neighbourhood $U\subset B$ with local coordinates $u^i$. Let $U\times \RR^n$ with the coordinates $(u^i,v^i)$, $v^i$ denoting the coordinates on $\RR^n$, be the local model for $M=TB$. We define the para-complex structure on $M$ in terms of its adapted coordinates $(x^i=u^i+v^i,\xt_j=u^k-v^k)$. The fact that $M$ is affine means that the transition functions are in $GL_n(\RR)\ltimes \RR^n$, i.e. of the form
\begin{align*}
    u^i\mapsto u'^i(u^i)=A_{\ j}^{i}u^j+B^i,\quad A \in GL_n,\ B\in \RR^n.
\end{align*}
This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $u^i\mapsto A^i_{\ j}u^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
\begin{align*}
    (x^i,\xt_j)\mapsto (A_{\ k}^{i}x^k+B^i,A_{\ k}^{j}\xt^k+B^j),
\end{align*}
which assures that the total space of $TB$ is an affine manifold with $(x^i,\xt^j)$ affine coordinates. In particular $(x^i,\xt^j)$ are adapted coordinates of an integrable para-complex structure on $TB$, because the transition functions are para-holomorphic.

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{\marginparwidth}
\addtolength{\headwidth}{0.25in}
%----------------
%\setlength{\marginparwidth}{0pt} % width of margin notes
%\setlength{\marginparsep}{0pt} % width of space between body text and margin notes
\setlength{\evensidemargin}{0.125in} % Adds 1/8 in. to binding side of all 
\setlength{\oddsidemargin}{0.125in} % Adds 1/8 in. to the left of all pages
\setlength{\textwidth}{6.375in} % assuming US letter paper (8.5 in. x 11 in.) and 
\raggedbottom
\setlength{\parskip}{\medskipamount}
\renewcommand{\baselinestretch}{1}
%---------------------------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\sA}{\mathcal{A}}
\newcommand{\cO}{\mathcal{O}}
\def\d{{\rm d}}
\def\dbar{\Bar{\partial}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{{\tl{L}}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\bm{\p}}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\theoremstyle{remark}
\newtheorem{question}[theorem]{Question}
\newenvironment{claim}[1]{\par\noindent\underline{Claim:}\space#1}{}
\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $[acksquare$}

\newtheoremstyle{examples}%                % Name
   {10pt}%                                     % Space above
   {10pt}%                                     % Space below
   {}%                                     % Body font
   {}%                                     % Indent amount
   {\bfseries}%                            % Theorem head font
   {:}%                                    % Punctuation after theorem head
   { }%                                    % Space after theorem head, ' ', or \newline
   {}%                                     % Theorem head spec (can be left empty, meaning `normal')
\theoremstyle{examples}
\newtheorem{Ex}[theorem]{Example}
\input xy

@@

This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like. First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle. The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
\begin{align}\label{para-holo-vector}
X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
\end{align}
i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.

@@

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}\label{isom_bigradings2}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

@@

\subsubsection{Lie algebroids of a para-complex manifold}\label{lie_algds_paracpx}
Here we briefly discuss what Lie algebroids the para-complex structure on a manifold $\PS$ gives rise to.
%First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$. The three satisfy the following:
%\begin{enumerate}
%\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
%\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
%\end{enumerate}

The first example is the tangent Lie algebroid
\begin{Ex}[Tangent Lie algebroid]\label{ex:tangent_lie}
The {\bf tangent Lie algebroid} exists on any manifold $\PS$ and is given by the data $E=T\PS$, $a=\id$ and $\brac_E=\brac$.
\end{Ex}

The following examples are of the same flavor, except we consider the subbbundle of the tangent bundle:
\begin{Ex}[Lie algebroids of para-complex eigenbundles]\label{ex:real-lie-algds-on-paracpx}
Let $(\PS,K)$ be a para-complex manifold with $\pm 1$ eigenbundles $L$ and $\Lt$. The following are Lie algebroids
\begin{enumerate}
\item $E=L$, $a=\imath_L:L\hookrightarrow T\PS$, $\brac_E=\brac\mid_L$, and
\item $E=\Lt$, $a=\imath_\Lt:\Lt\hookrightarrow T\PS$, $\brac_E=\brac\mid_\Lt$,
\end{enumerate}
%\begin{itemize}
%\item $E=TM\rightarrow M$, $a=\id_{TM}$, $\brac_E=\brac_M$, and
%\item $E=T\Mt\rightarrow \Mt$, $a=\id_{T\Mt}$, $\brac_E=\brac_\Mt$,
%\end{itemize}
where $\imath_{L/\Lt}$ are the inclusion maps and $\brac\mid_{L/\Lt}$ are the restrictions of the Lie bracket to $L$ and $\Lt$. The above are Lie algebroids in particular because $K$ is integrable so that $[L,L]\subset L$ and $[\Lt,\Lt]\subset \Lt$. Moreover, the two above Lie algebroids are exactly the tangent Lie algebroids of the integral foliations of $L$ and $\Lt$, $M$ and $\Mt$ respectively, once we restrict the module from $C^\infty(\PS)$ to $C^\infty(M)$ and $C^\infty(\Mt)$. Note that the two Lie algebroids exist individually on half-integrable almost para-complex manifolds.

The Chevalley-Eilenberg complexes of the two Lie algebroids are given by
\begin{enumerate}
\item $(\Lambda^\bullet L^*=\Lambda^{(\bullet,0)}(\PS),\p)$, and
\item $(\Lambda^\bullet \Lt^*=\Lambda^{(0,\bullet)}(\PS),\pt)$,
\end{enumerate}
where $\p$ and $\pt$ are defined by \eqref{paracomplex_dels}.
\end{Ex}

If we now consider the para-complexified tangent bundle $T\PS_\Cc$, we get a para-complex Lie algebroid, which can be understood as certain sense as a {\it sum} of the two above Lie algebroids:
\begin{Ex}[Para-holomorphic tangent bundle]\label{ex:para-hol-tangent}
The $+k$-eigenbundle $T^{1,0}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{1,0}$ and the anchor is again the inclusion $\imath:\  T^{1,0}\hookrightarrow T\PS_\Cc$. We can identify $T\PS_\Cc=T\oplus k T$, so that a section $X\in \XX_\Cc(\PS)$ is written as $X=U+kV=(U,V)$ for $U,V \in \XX(\PS)$ real vector fields and the Lie algebroid bracket is then given in terms of the usual Lie bracket of real vector fields as
\begin{align*}
[(U,V),(U',V')]=([U,U']+[V,V'],[U,V']+[V,U']).
\end{align*}
The Chevalley-Eilenberg complex is the para-complexified Dolbeault complex \eqref{para-dolbeault}.

There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{1,0}_\Cc(\PS)$ to a pair of vector fields
\begin{align*}
X=(U,V) \overset{\phi^{-1}}{\mapsto} (U+V,U-V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
\end{align*}
realizing the $\mathbb{R}$-linear isomorphism between $T^{1,0}$ and $T\PS=L\oplus \Lt$. This map can be used to map the para-complex Lie algebroid $T^{1,0}$ with a pair of real Lie algebroids. It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
\begin{equation*}
\begin{tikzcd}
T^{1,0} \arrow[hookrightarrow]{d}{\imath}\arrow{r}{\phi^{-1}} & L\oplus \Lt\arrow[hookrightarrow]{d}{\imath_L\oplus\imath_\Lt}\\
TP_\Cc \arrow{r}{(\text{Re},\text{Im})} & T\oplus T
\end{tikzcd}\ .
\end{equation*}
Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular is not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.

Consequently, the Chevalley-Eilenberg complex then also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
\end{Ex}

\begin{remark}
The Lie algebroid described above is again analogous to the complex Lie algebroid $T^{1,0}\subset T_{\mathbb{C}}M$ over a complex manifold $(M,I)$. The crucial difference is that because $I$ does not give rise to a splitting of the real bundle $TM$, there is no correspondence to a pair of real Lie algebroids as in the para-complex case.
\end{remark}

@@

We start with a recollection of Calabi-Yau manifolds. For more details, the reader may consult for example the book \cite{joyce2000compact}. There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we choose the following:
\begin{Def}
A Calabi-Yau manifold is a K\"ahler manifold $(M,g,I)$ of complex dimension $d$ such that the holonomy group of the underlying Riemannian metric $g$ is $\text{Hol}(g)\subseteq SU(d)$.
\end{Def}
Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.

Remember that on any K\"ahler manifold we have $\text{Hol}(g)\subseteq U(d)$. A consequence of the property $\text{Hol}(g)\subseteq SU(d)\subset U(d)$ is that there exists a covariantly constant, non-vanishing section $\Omega \in \Omega^{(d,0)}(M)$ called the {\it holomorphic volume form}. On $\mathbb{C}^d$, the structures $(g,\omega,\Omega)$ take in the canonical holomorphic coordinates the form:
\begin{align*}
    g=\sum_{i=1}^d dz^i\otimes d\bar{z}^i,\quad \omega=\dfrac{i}{2}\sum_{i=1}^d dz^i\w d\bar{z}^i,
 \quad   \Omega=dz^1\w\cdots\w dz^d.
\end{align*}
We can describe $\Omega$ in coordinate-independent way as follows:
\begin{lemma}\label{lem:CY}
Let $(M,g,I)$ be a Calabi-Yau manifold of complex dimension $d$ and $\omega=gI$ the fundamental form. There exists a nowhere vanishing section $\Omega \in \Omega^{(d,0)}(M)$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
\begin{align*}
    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega}.
\end{align*}
\end{lemma}

@@

Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form. Consider the canonical para-K\"ahler structure on $\RR^{2d}$
\begin{align*}
    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i,
\end{align*}
which is preserved by $GL(d)$. Introducing the following constant tensor
\begin{align*}
    \hat{\Omega}=dx^1\w\cdots\w dx^d+d\xt_1\w\cdots\w d\xt_d=\Omega+\tl{\Omega},
\end{align*}
we see that the triple $(\eta,\omega,\hat{\Omega})$ is preserved exactly by $SL(d)$ and $\hat{\Omega}$ satisfies
\begin{align*}
   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
\end{align*}
Therefore, we have the analogue of Lemma \ref{lem:CY}:
\begin{lemma}
Let $(\PS,\eta,K)$ be a para-Calabi-Yau manifold of dimension $2d$ and $\omega=\eta K$ the fundamental form. There exists a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega}) \in\Omega^{(d,0)+(0,d)}(\PS)$ that is para-holomorphic, $\pt\Omega=\p\tl{\Omega}=0$ and satisfies
\begin{align*}
   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
\end{align*}
\end{lemma}
\begin{proof}
The proof is exactly analogous to the complex case, see for example \cite[Lemma~4.4]{Joyce:2001xt}.
\end{proof}

Remember that on a para-complex manifold $\PS$ of dimension $2n$, the appropriate analogue of the holomorphic forms are the para-holomorphic forms, given by pairs $(\alpha,\tl{\alpha})\in\Omega^{(k,0)+(0,k)}(\PS)$ (here the bigrading is with respect to the para-complex structure), satisfying $\pt\ap=\p\tl{\ap}=0$. Therefore, the {para-holomorphic volume form} is exactly the correct analogue of the holomorphic volume form in case of the Calabi-Yau manifolds. Furthermore, because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, and so it defines a volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and we see that the para-Calabi-Yau structure on $\PS$ augments the canonical foliations $M$ and $\Mt$ of the para-complex manifold with volume forms and both the foliation manifolds are consequently orientable.

@@

\begin{Ex}
If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
We will denote this dg manifold by $N_{\pd}$. 
To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\hat{\Omega_N}$.

The Lie algebroid whose Chevalley-Eilenberg complex is the para-complex Dolbeault complex is the para-complex Lie algebroid on the para-Holomorphic tangent bundle $T^{0,1}$ described in Example \ref{ex:para-hol-tangent}.
%The differential on the
\end{Ex}

@@

\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the usual Calabi-Yau geometry of $M$. Consider an affine manifold $B$ and take a neighbourhood $U\subset B$ with local coordinates $u^i$. Let $U\times \RR^n$ with the coordinates $(u^i,v^i)$, $v^i$ denoting the coordinates on $\RR^n$, be the local model for $M=TB$. We define the para-complex structure on $M$ in terms of its adapted coordinates $(x^i=u^i+v^i,\xt_j=u^k-v^k)$. The fact that $M$ is affine means that the transition functions are in $GL_n(\RR)\ltimes \RR^n$, i.e. of the form
\begin{align*}
    u^i\mapsto u'^i(u^i)=A_{\ j}^{i}u^j+B^i,\quad A \in GL_n,\ B\in \RR^n.
\end{align*}
This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $v^i\mapsto A^i_{\ j}v^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
\begin{align*}
    (x^i,\xt_j)\mapsto (A_{\ k}^{i}x^k+B^i,A_{\ k}^{j}\xt^k+B^j),
\end{align*}
which assures that the total space of $TB$ is an affine manifold with $(x^i,\xt^j)$ affine coordinates. In particular $(x^i,\xt^j)$ are adapted coordinates of an integrable para-complex structure on $TB$, because the transition functions are para-holomorphic.
